A generalized model for the charge transport properties of dressed quantum Hall systems

### 2021-11-18 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Update res paper

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions. This is not an overly restrictive assumption and others have used the same assumption in their work, e.g. see \textit{et al.} \cite{endo09}.
} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to

@@

Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage. The  change of the gate voltage applied to the system will modify the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature. By comparing these empirical observations with our results given in Fig.~\ref{fig:4}, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value. Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased. This will locate to the Fermi level on higher-order Landau levels. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78} as well.}

@@

{\color{Red}
Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems. Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
}
%===============================================================================

%===============================================================================
% Section 07 : Physical significance of the outcome
%===============================================================================
{\color{Red}
\section{\label{sec:physical_significance} Physical Significance of the Outcomes}
With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations. \cite{endo09,wakabayashi78}.

Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions. As illustrated in Fig.~\ref{fig:4}, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model. Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}. However, from our results given in Fig.~\ref{fig:5}, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field. In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.

Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system. We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity. A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}. In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures. Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.~\ref{fig:4}. However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.

The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices. Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
}
%===============================================================================

@@

In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. {\color{Red}
We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions. Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}

Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels. {\color{Red}Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}. This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.}

@@

First, we consider the $x$-directional particle current operator component, and we can identify that as
\begin{equation} \label{eq:d4}
  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
\end{equation}
Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
\begin{equation} \label{eq:d5}
  \left({j}_x \right)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
\end{equation}
and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
\begin{equation} \label{eq:d6}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} = &
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int
    \left(\hbar k'_x + eBy\right) \\
    & \times
     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    dy.
  \end{aligned}
\end{equation}
Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
\begin{equation} \label{eq:d7}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} =
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int &
    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
    & \times
    \chi_{n}(\bar{y})
    \chi_{n'}(\bar{y})
    d\bar{y}.
  \end{aligned}
\end{equation}
Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
\begin{equation} \label{eq:d8}
  \int \chi_{n}({y})
  \chi_{n'}({y}) d{y} = \delta_{n',n},
\end{equation}
\begin{equation} \label{eq:d9}
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
    \frac{1}{\kappa}
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
\end{equation}
we simplify the matrix elements of $x$-directional current operator to obtain
\begin{equation} \label{eq:d10}
  \begin{aligned}
    &\left({j}_x \right)_{nm,n'm'} =
    \frac{eB}{{\widetilde{m}}\kappa}
    \delta_{k_x,k'_x} \\
    & \qquad\times
    \left[
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}\right)
    + \zeta(t) \delta_{n',n}
    \right].
  \end{aligned}
\end{equation}
Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
\begin{equation} \label{eq:d11}
  \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =&
      \frac{eB}{\widetilde{m}\kappa}
      \delta_{k_x,k'_x} \\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right).
  \end{aligned}
\end{equation}
For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
\begin{equation} \label{eq:d12}
  \begin{aligned}
      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
      \frac{e\hbar}{{m_e}l_0}
      \delta_{k_x,k'_x}\\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right),
  \end{aligned}
\end{equation}
where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.

>>>>

In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
{\color{Red}
It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions. This is not an overly restrictive assumption and others have used the same assumption in their work, e.g. see \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to

@@

Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
The applied gate voltage to the system modifies the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}

@@

{\color{Red}
Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems. Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
}
%===============================================================================

%===============================================================================
% Section 07 : Physical significance of the outcome
%===============================================================================
{\color{Red}
\section{\label{sec:physical_significance} Physical Significance of the Outcomes}
With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.

Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig.~\ref{fig:5} that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}. Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures. Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.~\ref{fig:4} depicts this result.
In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.

The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
magneto-transport properties of 2D nanostructures.
}
%===============================================================================

@@

In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. {\color{Red}
We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.

Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels. {\color{Red}Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref. \cite{endo09}. The authors of Ref. \cite{dini16} have used the conventional expression of longitudinal conductivity from Refs. \cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels. These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.}

@@

First, we consider the $x$-directional particle current operator component, and we can identify that as
\begin{equation} \label{eq:d4}
  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
\end{equation}
Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
\begin{equation} \label{eq:d5}
  \left({j}_x \right)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
\end{equation}
and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
\begin{equation} \label{eq:d6}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} = &
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int
    \left(\hbar k'_x + eBy\right) \\
    & \times
     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    dy.
  \end{aligned}
\end{equation}
Let $[y - y_0 - \zeta(t)] = \bar{y}$, and we can obtain
\begin{equation} \label{eq:d7}
  \begin{aligned}
    \left({j}_x \right)_{nm,n'm'} =
    \frac{1}{{\widetilde{m}}}
    \delta_{k_x,k'_x}
    \int &
    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
    & \times
    \chi_{n}(\bar{y})
    \chi_{n'}(\bar{y})
    d\bar{y}.
  \end{aligned}
\end{equation}
Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
\begin{equation} \label{eq:d8}
  \int \chi_{n}({y})
  \chi_{n'}({y}) d{y} = \delta_{n',n},
\end{equation}
\begin{equation} \label{eq:d9}
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
    \frac{1}{\kappa}
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
\end{equation}
we simplify the matrix elements of $x$-directional current operator to obtain
\begin{equation} \label{eq:d10}
  \begin{aligned}
    &\left({j}_x \right)_{nm,n'm'} =
    \frac{eB}{{\widetilde{m}}\kappa}
    \delta_{k_x,k'_x} \\
    & \qquad\times
    \left[
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}\right)
    + \zeta(t) \delta_{n',n}
    \right].
  \end{aligned}
\end{equation}
Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression. Therefore, we can identify the $0$-th component of the Fourier series as
\begin{equation} \label{eq:d11}
  \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =&
      \frac{eB}{\widetilde{m}\kappa}
      \delta_{k_x,k'_x} \\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right).
  \end{aligned}
\end{equation}
To calculate the electric current operator, we substitute the electron’s charge and effective mass to the above derived equation. This leads to
\begin{equation} \label{eq:d12}
  \begin{aligned}
      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
      \frac{e\hbar}{{m_e}l_0}
      \delta_{k_x,k'_x}\\
      & \times
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1} \right),
  \end{aligned}
\end{equation}
where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.
